### 2014-07-01 Equipment_and_Testing_Guide/Equipment_and_Testing_Guide.tex
Equipment Guide: Minor edit to testing procedure
Equipment Guide: Minor edit to test procedure

\begin{itemize}
\item Power on the following devices:
    \begin{itemize}
    \item Generators (check oil and gas levels)
    \item Uninterruptible Power Supplies (UPSs)
    \item WiFi routers/repeaters
    \item Arduino laptop with NTP, RabbitMQ, Python receive\_data.py script
    \item DAQs and laptops
    \item Weather stations
    \item Gas analyzers (leave running as long as possible during testing)
    \item Digital video recorder (DVR)
    \item Bullet cameras and power supplies
    \item Thermal imaging cameras (TICs)
    \item Digital video cassette recorders (DVCRs)
    \item GoPros
    \item Video cameras
    \end{itemize}
\end{itemize}

@@

\begin{itemize}
\item Synchronize time on DAQ computers and digital video recorder

@@

\item Check and record lag time on gas analyzer probes

>>>>

\begin{itemize}
\item Power on the following devices:
    \begin{itemize}
    \item Generators (check oil and gas levels)
    \item Uninterruptible Power Supplies (UPSs)
    \item WiFi routers/repeaters
    \item Arduino laptop with NTP, RabbitMQ, Python receive\_data.py script
    \item DAQs and laptops
    \item Weather stations
    \item Gas analyzers (leave running as long as possible during testing)
    \item Digital video recorder (DVR)
    \item Bullet cameras and power supplies
    \item Thermal imaging cameras (TICs) (check battery levels)
    \item Digital video cassette recorders (DVCRs) (check battery levels)
    \item GoPros (check battery levels)
    \item Video cameras (check battery levels)
    \end{itemize}
\end{itemize}

@@

\begin{itemize}
\item Synchronize clock time on DAQ computers, digital video recorder, etc.

@@

\item Record serial number and probe location of gas analyzers; check and record lag time
